(TEMP) Online Video Game Monetization Schemes and Its Relationship to the Consumers

### 2022-04-27 outputs/paper/paper.Rmd
Finished Discussion and Limitation Section in paper.Rmd. Added Activision Blizzard's Q42021 earnings PDF in inputs/literature.

The statistics presented in Table \@ref(tab:table3) suggests that
the amount of revenue obtained from game package purchases is relatively
minuscule compared to other sources of income. Therefore, publishers of
MMORPGs should forgo charging an upfront fee for their games in order to draw
in more players so that they can browse the much more profitable in-game cash
shop instead.

TODO; speculations as to why we saw a particular trend, its implications.
Limitations. Further Directions.

>>>>

The statistics presented in Table \@ref(tab:table3) suggests that
the amount of revenue obtained from game package purchases is relatively
minuscule compared to other sources of income. This raises the question
of whether publishers of MMORPGs should forgo charging an upfront fee
for their games in order to draw in more players so that they can browse
the much more profitable in-game cash shop instead.

From a pure-revenue standpoint, there is a debate to be made about whether
or not a video game publisher
should charge an upfront cost on consumers for access to their game.
On one hand, giving concrete price tags to a game before its launch would grant
the publisher the strategy to let consumers pre-order the game, injecting a
massive amount of funding into the company that could be used for future
developments and investments on other projects well before they even need to
finish and release the game.
On the other hand, price tags too high may discourage consumer interest in the
game, preventing them from ever engaging with the in-game cash shop which
is much better suited for long-term revenue generation.

MMORPGs have a unique way to circumvent this dilemma by releasing the game
with a price tag and removing the said price tag later down the line. Due to
their progression-based nature and continuous development, consumer interest in
MMORPGs is usually expected to remain consistently high past its initial
launch period. As such, there is less worry about upfront price tags 
dissuading large amounts of potential players during the launch; High
interest in the game post-launch should ensure continued influx of players
who will have a chance to interact with the game's cash shop once the
upfront cost is dropped.

As discussed in Section \@ref(free-game-package), roughly 66% of players who obtained
the free package for the game ended up spending real world currencies in the
pearl shop. This shows that the majority of players will spend money on a game
even when it is free-to-play, providing further incentives for MMORPG publishers
to abandon charging upfront fees.

## Number of Subscription Items

The three types of subscription items in BDO--Value Pack, Blessing of Kamasylve,
and Secret Book of Old Moon--each offer a different set of bonuses relatively
independent from each other. This means that some players may prefer
certain bonuses over others and may not purchase all three subscription items
at once. As discussed in Section \@ref(subscription-items), BK and OM are generally
rated as less important than VP;
BK and OM also account for less than half of the revenue
generated by VP on average, as demonstrated in Table \@ref(tab:table3).

The lack of interest in BK and OM could be due to their status as subscription
items introduced later than the VP. This means that the set of bonuses they
grant must be separate from those granted by the VP, which was initially the
only subscription item in the game. This need to avoid overlaps in bonuses may
have caused BK and OM to be to designed to grant less generally
useful bonuses as the vital ones are already covered by the VP.

Another potential reason to this disinterest is the difference in price between
BK and OM, and VP: Without any discounts, 30 days of VP costs 1500 pearls
(roughly \$15.00 USD) while 30 days of BK/OM costs 2500 pearls (roughly \$25.00
USD), an increase in price by roughly 66%. There is no plausible explanation
as to why BK/OM are priced higher than VP except publisher bias; While most
players regard VP as the more important subscription item (as shown in Figure
\@ref(fig:graph9)), publishers of the game may simply think otherwise.
If possible, further extensions on this study should inquire the players about
their reasons for rating certain subscription items less important, be it the
price of its bonuses.

While the statistics seem to suggest that the introduction of
multiple subscription items for a single game is not an optimal strategy, this
type of item does not require a lot of development resources from the developers
to create and is a relatively effortless way to generate revenue.
Therefore, the addition of new subscription items beyond the first one
into a game is not unadvised but rather simply less profitable than the first
one is.

## Whales

According to Connick [@citebalance], `whale` is originally a term in sales
used to refer to clients that bring in substantially more business than
an average client does.
The video game industry has borrowed this termto refer to players
who spend an exorbitant amount of real world currency in a game.
As alluded to in the beginning paragraphs of Section
\@ref(preliminary-analysis), we
observer several outliers in the dataset with drastically more in-game spending
than the rest of the respondents. These outliers are most likely the
aforementioned whales.

Whales are often make up a major portion of a video game's revenue:
For example, according to Activision Blizzard's [@citeacti] 2021 fourth quarter
revenue release,
the company made a net revenue of \$8.086 billion USD, \$5.736 billion USD of
which is from in-game transactions and subscriptions. A surprising high 70.94%
of total revenue for the company is from sources other than upfront costs.

```{r table4, echo=FALSE, warning=FALSE, message=FALSE}
summary_tbl3 <- cleaned_data |>
  summarise(ps_percent = mean(ps_total)/(mean(ps_total)+mean(packages_usd)),
            pack_ps_percent = mean(packages_usd)/(mean(ps_total)+mean(packages_usd)))

# Use kable to create the table
summary_tbl3 |>
  kable(
    caption = "Summary of Average Percentage of Spending on Pearl Shop and Packages",
    col.names = c("Pearl Shop",
                  "Game Packages"),
    digits = 4,
    booktabs = TRUE,
    linesep = ""
  ) |>
  add_header_above(c("Spending Percentage" = 2))
```

As Table \@ref(tab:table4) shows, if we do not exclude the whales as outliers
from the dataset, then the average
revenue generated from the pearl shop accounts for roughly 95% 
This clearly demonstrates the importance of whales to a video game company's
profit, and why catering to these whales could often result in more profit
than focusing on satisfying to the average consumer.

Whales are very rare compared to the average player. Unfortunately,
due to the limited
number of responses generated by the survey, 
an analysis on whales in particular was
not able to be conducted in this paper. Possible extensions of this paper could
focus on gathering a large enough dataset in the hopes that it contains a
sufficient sample of whale respondents to fit a model to.

## Limitations

As discussed in Section \@ref(whales), the rarity of whales and the limited
sample size of the dataset means that the analysis in this paper could not
incorporate whales effectively into the model. Should a large enough sample size
for whales be collected, a model specifically designed to analyze whale spending
is a great extension for this paper.

As mentioned in Section \@ref(survey-design), Pearl Abyss does not have any
public APIs available for tracking user's spendings, playtime, and character
counts, etc. This is understandable as it could be considered sensitive
information. However, Pearl Abyss also does not include detailed and/or easily
accessible information trackers for the players themselves. Players cannot
access a detailed breakdown of the composition of their spending, nor can they
calculate exactly how long they have played the game for save for a few
milestone achievements at large intervals of playtime (500 days, 1000 days,
etc). Respondents who played the game on the game distribution platform Steam
has less issues with this as Steam offers them playtime trackers as well as
access to their total spending on the game, though the composition of the
spending is still not recorded. The problem caused by this is that respondents
have to estimate their playtime and the composition of their spending to the
best of their ability. As such, most monetary statistics in the dataset
have some level of estimation involved in them except total spending in pearl
shop and total spending on game packages. Should Pearl Abyss publish an API
in the future for the game, future analyses will no longer need to rely on
convenience sampling and could instead employ better sampling strategies that
more accurately represent the true population.
